Energy Dependence of Synchrotron X-Ray Rims in Tycho's Supernova Remnant

### 2014-12-10 manuscript/paper-tycho.tex
Eyeball fits to VLA regions; new figs, paper
Manual profile fits for all VLA/X-ray regions, in plaintext and ipynb
Clean ipynb for radio prfs, generate ms figs
Paper draft updated and sent out

%\documentclass[manuscript]{aastex}  % one-column, double-spaced GENERATE BIB
%\documentclass[12pt,preprint]{aastex}  % one-column, single-spaced
%\documentclass[iop, apj, numberedappendix, twocolappendix]{emulateapj}
\documentclass[iop, apj, numberedappendix]{emulateapj}

% Customize figures/sizing for 2 column vs. manuscript printout
\usepackage{etoolbox}
\newtoggle{manuscript}
%\toggletrue{manuscript}
\togglefalse{manuscript}

@@

\begin{abstract}
Several young supernova remnants exhibit thin X-ray bright rims of synchrotron
radiation at their forward shocks.  Thin rims have been taken to indicate that
shock-accelerated electrons rapidly cool downstream of the shock, requiring
strong magnetic field amplification.  But, magnetic field damping immediately
behind the shock could produce similarly thin rims.  We measured rim widths
around Tycho's supernova remnant in 5 energy bands using an archival $750
\unit{ks}$ \Chandra observation.  Rims consistently narrow with increasing
energy and are well-described by either loss-limited or magnetically damped
scenarios, hence X-ray rim widths alone cannot discriminate between models.
Loss-limited fits require amplified magnetic fields of $\abt200$--$1000 \muG$
and particle diffusion coefficients $\abt1$--$100\times$ Bohm values,
consistent with prior work on Tycho's SNR, whereas magnetic damping permits
magnetic fields of $\abt 10$--$300 \muG$ and comparatively smaller diffusion
coefficients (typically $\abt 1$--$10$).  Diffusion coefficients, magnetic
field strengths, and magnetic damping lengthscales are somewhat degenerate in
setting observed rim widths and drop-offs.  Although we cannot discriminate
from width measurements alone, a combined study of X-ray and radio profiles may
break the observed degeneracies to confirm or rule out turbulent magnetic field
damping downstream of supernova remnant shocks.
\end{abstract}

@@

% TODO GENERAL WARNING -- DATA MAY NOT ALL BE FULLY CONSISTENT AT THIS TIME.
% (spectra/profiles/fwhms/fits).

@@

% Could just discuss one model...
%We consider two particle transport models that we fit to measurements of
%Tycho's thin rim widths.  We measure the rim full widths at half maximum
%(FWHMs) (Section~\ref{sec:fwhms}) and compare our measurements to the transport
%model predictions of rim FWHMs at multiple photon energies, for various input
%parameters.  The models accept four free parameters: magnetic field strength
%$B_0$, a scaled diffusion coefficient $\eta_2$, a diffusion-energy scaling
%exponent $\mu$, and a magnetic damping lengthscale $a_b$ (an $e$-folding
%length).

% Twiddle-ables in our model (the most useful part, since just modeling
% alone don't do much)
%Our model fitting explores the space of varying diffusion (a bulk
%representative of the underlying MHD turbulence and what have you)
%and considers the two scenarios of constant magnetic field (resulting in
%so-called loss-limited rims) and a damped field that falls off exponentially
%behind the forward shock, as suggested by \citet{pohl2005}.
% this might go at the front before we launch into model details.

@@

%Different types of MHD turbulence may give rise to a non-linear energy
%scaling for diffusion coefficient instead \citep{giacalone1999, reynolds2004}.
%Power-wavenumber spectra for Kolmogorov and Kraichnan turbulence, with a
%quasi-linear approximation for particle motion,
%\note[Aaron]{I don't really know what this means}
%predict $D \propto E^{1/3}$ and $D \propto E^{1/2}$ respectively.
%Particle gyroradii larger than field coherence length may also lead to
%$D \propto E^{2}$ \note[Aaron]{Source?? Parizot mentions this in one sentence
%and cites nothing.  I have no idea what this means.}

@@

\begin{figure}
    \centering
    \iftoggle{manuscript}{
        %\includegraphics[width=0.5\textwidth]{figures/f0-snr-inv.png}
    }{
        %\plotone{figures/f0-snr-inv.png}
        \plotone{figures/snr.pdf}
    }
    \caption{RGB image of Tycho with region selections overlaid.  Image bands
    are 0.7--1 keV (red), 1--2 keV (green) and 2--7 keV (blue).  Bold region
    labels (1, 16) indicate region selections shown in
    Figures~\ref{fig:spec},~\ref{fig:profiles}.  Filament 1: Regions 1--3,
    filament 2: regions 4--10, filament 3: regions 11-13, filament 4:
    regions 14--17, filament 5, regions 18--20.
    \label{fig:snr}}
\end{figure}
% NOTE keep region # bolding updated to match displayed filaments

@@

% NOTE keep blacklisted/excluded region count updated!
From the fitted profiles we extracted a full width at half maximum (FWHM) for
each region and each energy band after subtracting a constant background term
$\min(C_u, C_d)$.  We could not resolve a FWHM in 4 of 20 regions at 0.7--1 keV
(Table~\ref{tab:fwhms}); in these regions, either the downstream FWHM bound
would extend outside the fit domain or we could not find an acceptable fit to
equation~\eqref{eq:prof}.  We were able to resolve FWHMs for all regions at
higher energy bands (1--7 keV).
% NOTE review the FWHM rejection criterion, on the final set of regions
% We will be blacklisting by hand, and we have to explain how we chose the
% blacklisted ones.

@@

% How we ran model fits (itemize knobs, explain energy band mapping, errors,
% fitting procedure
We fit model FWHM predictions given by Equation~ \eqref{eq:model} to our
measured rim widths as a function of energy by varying several physical
parameters: magnetic field strength $B_0$, normalized diffusion coefficient
$\eta_2$, diffusion-energy scaling exponent $\mu$, and minimum field strength
$\Bmin$ and lengthscale $a_b$ for a damped magnetic field scenario.  We
mapped each width measurement to the lower energy limit of its energy band;
e.g., $0.7$--$1 \unit{keV}$ is assigned to $0.7 \unit{keV}$ and fitted to model
profile widths at $0.7 \unit{keV}$.  Width errors in our least squares fits
average the positive and negative errors on each FWHM measurement.  For an
input set of model parameters, we numerically computed intensity profiles and
hence model FWHMs as detailed in Section~\ref{sec:transport}, and used a
Levenberg-Marquardt fitting routine to identify best fit model parameters.
To assist the nonlinear fitting, we tabulated model FWHM values on a large grid
of model parameters (primarily $\eta_2$ and $B_0$) and used best-fit grid as
initial guesses for fitting.
% TODO this may be obsoleted if we recompute stuff...  I only computed errors
% on the loss-limited model, and those fits are now out of date too...
Errors on best fit parameters were computed by varying each fit parameter and
obtaining a new best fit model, with one less degree of freedom, to find the
parameter limit such that $\Delta \chi^2 = 1$ for a roughly 1-$\sigma$ error.

@@

% ----------------------------------------
% Constraining rims via radio measurements
% ----------------------------------------
\subsection{Radio rims constrain damping scenarios}

The presence of thin radio rims in Tycho may help constrain magnetic field
damping.  Radio emission in Tycho arises from the same population of
shock-accelerated electrons generating nonthermal X-ray rims.  But, $\abt$GeV
electrons have cooling times of order $10^5$--$10^7 \unit{yr}$ in $10$--$100
\muG$ magnetic fields.  Despite the extended population of radio synchrotron
electrons, radio rims and decreases in emission intensity immediately behind
the shock may be explained by magnetic damping.  If remnant-wide diffuse
emission near the forward shock increases monotonically towards the center of
the remnant, only magnetic field damping can cause emission to decrease.  A
loss-limited field predicts monotonically increasing emission downstream of the
forward shock in our steady-state transport model.

We extract radio profiles from a $1.375 \unit{GHz}$ image of Tycho taken
with the VLA in A configuration in March 1994 (PI: D. Moffett); see
\citet{reynoso1997} for a detailed presentation.
\emph{Was data from all configurations merged?  Done by \citet{reynoso1997}.}
The half-power beam width of $\abt 1.5\arcsec$ just resolves thin radio rims
and structure near the forward shock; the image is sampled at $0.5\arcsec$.  We
shift radio profiles forward by $9\arcsec$ to correct for proper motion,
assuming an $0.3\arcsec/\mt{yr}$ expansion rate \citep{katsuda2010-tycho}.
Figure~\ref{fig:radio-snr} shows the extraction regions overlaying the radio
image and the previous X-ray profile regions of Figure~\ref{fig:snr}.

@@

\subsubsection{Combined radio and X-ray profile fitting}

%% TODO Working at around here...  now pending some code work.

Figure~\ref{fig:radio-prfs} shows extracted radio and nonthermal X-ray
($4$--$7\unit{keV}$) profiles from the plotted regions (Figure~\ref{fig:snr}),
shown in Figure~\ref{fig:radio-prfs}.  The radio profiles show a range of
morphology, including thin rims with a trough and either increasing and
decreasing emission towards the remnant interior.

\begin{figure}
    \centering
    \plotone{figures/radio-prfs-subplot.pdf}
    \caption{Radio (red) and nonthermal X-ray (blue) intensity profiles from
    extraction regions shown in Figure~\ref{fig:radio-snr}.  Radio profiles are
    shifted forward by $9\arcsec$ to correct for proper motion.  Both X-ray and
    radio profiles are translated to place the $4$--$7 \unit{keV}$ rim $\abt
    2\arcsec$ behind the forward shock radius $r_s = 240\arcsec$.  We emphasize
    that the intensities and radial coordinate translations are chosen strictly
    to aid visual comparison and are otherwise arbitrary.
    \label{fig:radio-prfs}}
\end{figure}

Our model profiles are fully characterized by $B_0$, $a_b$, and $B_{\mt{min}}$,
with $B_{\mt{min}} = 5 \muG$ fixed as before.  We neglect diffusion in modeling
radio emission as particle energies are 3 orders of magnitude lower than in
X-ray.  This also circumvents the unphysical assumption that $D(x) B^2(x)$ is
constant, which was accepted in order to obtain Green's function solutions for
our transport model, equation~\eqref{eq:model}.  But, as we previously assumed
Bohm-like diffusion, another model for particle diffusion may be necessary at
radio wavelengths.

Radio emission profiles in Tycho have been modeled by \citet{cassam-chenai2007}
and \citet{morlino2012} as part of broader hydrodynamic modeling studies,
which permits modeling of emission throughout the remnant rather than just
behind the shock.  Although a full time-dependent model may better capture all
radio emission and nonthermal X-ray emission simultaneously, our simplified
model should capture the essential physics for a very young remnant such as
Tycho, for which the forward shock should be adiabatic.

We extracted hard X-ray pro

The distinct profile shapes of radio thin rims and rising or falling emission
behind the thin rims, if rims are present, may be more sensitive discriminants
of loss-limited and damping models.

In particular, our best fits to data with moderate $\mE$ generally require
small magnetic field $B_0$ and comparatively strong emission downstream of the
thin rim, just below the rim half-maximum.  Although the FWHMs accorded with
those of the loss-limited, the profiles were quite different
(Figure~\ref{fig:rims}).

\subsubsection{Radio rim shape analysis}

Although radio and X-ray rim profiles are difficult to jointly model, we can
use observed decreases in emission just behind the shock to constrain allowable
model parameters.  Where a decrease in radio emission occurs behind the peak
emission, the steepest decrease in emission allows us to bound the minimum
magnetic field and the maximum allowable damping length -- i.e., we require a
fast magnetic field drop-off with distance (for the assumed $B_{\mt{min}} = 5
\muG$).

Conversely, a continuous increase in emission requires a minimum damping
length, as too small a damping length and moderate field strength will give
rise to a radio rim.  However, diffuse remnant-wide radio emission may obscure
a radio rim associated with the forward shock.  Thus, although a continuous
rise in emission is consistent with weak damping (and loss-limited X-ray rims),
we cannot rule out the possibility of magnetic damping.

Table~\ref{tab:???} lists intensity drop-offs for radio and X-ray profiles in
each region at various distances behind the peak (rim) emission, favoring the
shortest possible distance to obtain a steep drop-off and better constrain
$B_0$ and $a_b$.  Assuming $B_0 < 500 \muG$ in a damped model, we can also
constrain the minimum

Generate a slew of profile shapes, and ask that emission over XXX distance
behind the shock NOT rise above the peak/rim distance.  This rules out the
smallest damping lengths and fields (i.e., no trough at XXX distance...)

Finally, if a trough is present in the radio rim, we may further

In Figure~\ref{fig:radio-bound} we illustrate schematically

\begin{figure}
    \centering
    \plotone{figures/radio-min-bound-6arcsec.pdf}
    \caption{Maximum intensity drop-off within 6 arcsec of forward shock for
        modeled 1.375 GHz radio profile.
    \label{fig:radio-bound}}
\end{figure}

@@

The exponential variation in $D(x)$ (equation~\eqref{eq:ddamp}) may not be
physically reasonable; as we have noted above, the assumption $D(x)
\propto 1 / B^2(x)$ gives rise to sharp gradients in diffusion coefficient and
even inverts the effect of $\eta_2$ on our model profiles (where larger
$\eta_2$ can cause rim widths to narrow).

However, the radio modeling assumes \emph{no diffusion} and should not be
impacted by this potentially incorrect assumption.

@@

We measured the widths of thin synchrotron filaments around Tycho's supernova
remnant and confirmed that our measured filaments are dominated by nonthermal
emission with clearly measurable full widths at half maximum in 4--5 energy
bands.  We find moderate narrowing of rim widths across the remnant,
corroborating rim narrowing observed by \citet{ressler2014} in the remnant of
SN 1006.  Our multiple measurements give loss-limited diffusion and magnetic fields
broadly consistent with prior estimates from rim widths
\citep[e.g.,][]{parizot2006, rettig2012} and radio and gamma ray measurements
\citep{acciari2011, morlino2012}.  Loss-limited and magnetic damping models are
equally capable of describing our observed data.  At small energy dependence
the two models are indistinguishable and magnetic damping fits still favor
moderately amplified magnetic fields.  At moderate energy dependence ($\mE \sim
-0.3$), the damping model favors weaker magnetic fields, but modeled FWHMs may
not be truly representative of thin rim widths and profiles.

As our data are not count limited, we suggest that additional proxies for
diffusion and magnetic field are needed to establish or rule out the presence
of damping at the shocks of young supernova remnants.  More sophisticated
modeling of shock physics \citep[e.g.,][]{zirakashvili2014} and shock/filament
structure \citep[cf.][]{caprioli2013} may be necessary to improve modeling
results.  Complete rim profile fitting and sub-arcsecond radio profiles (as may
be enabled by EVLA and ALMA) may better discriminate between models.

% Further work -- radio
%As has been noted by many workers, observations of radio synchrotron rims would
%provide strong and immediate evidence for magnetic field damping (at the
%lengthscales of said radio rims).  Previous workers have certainly tried
%\citep{cassam-chenai2007, morlino2012} but it seems not easy.
%A new epoch of VLA and \Chandra observations in this year (PIs: J. Hewitt, B.
%Williams) will offer a rich dataset of sub-arcsecond observations that may
%reveal more about rim morphology and perhaps even temporal variation over a 10+
%year baseline (compare to \citet{katsuda2010-sn1006}).

@@

A.T. thanks CRESST for sponsorship/support at GSFC (any relevant grants?)
B.J.W. NPP?
The scientific results reported in this article are based on data obtained from
the \Chandra Data Archive.
This research made extensive use of NASA's Astrophysics Data System.
This research made use of APLpy, an open-source plotting package for Python
hosted at \href{http://aplpy.github.com}{http://aplpy.github.com}.

@@

Here we supply detailed best loss-limited and damped fit results for averaged
filament widths in SN 1006, from \citet{ressler2014}.

>>>>

\documentclass[manuscript]{aastex}  % one-column, double-spaced GENERATE BIB
%\documentclass[12pt,preprint]{aastex}  % one-column, single-spaced
%\documentclass[iop, apj, numberedappendix, twocolappendix]{emulateapj}
%\documentclass[iop, apj, numberedappendix]{emulateapj}

% Customize figures/sizing for 2 column vs. manuscript printout
\usepackage{etoolbox}
\newtoggle{manuscript}
\toggletrue{manuscript}
%\togglefalse{manuscript}

@@

% TODO define loss-limited properly...
% ~210 words -- a little too long
\begin{abstract}
Several young supernova remnants exhibit thin X-ray bright rims of synchrotron
radiation at their forward shocks.  Thin rims have been taken to indicate that
shock-accelerated electrons rapidly cool downstream of the shock, requiring
strong magnetic field amplification.  But, magnetic field damping immediately
behind the shock could produce similarly thin rims.  We measured rim widths
around Tycho's supernova remnant in 5 energy bands using an archival $750
\unit{ks}$ \Chandra observation.  Rims consistently narrow with increasing
energy and are well-described by either loss-limited or magnetically damped
scenarios, hence X-ray rim widths alone cannot discriminate between models.
Loss-limited fits require amplified magnetic fields of $\abt200$--$1000 \muG$
and particle diffusion coefficients $\abt1$--$100\times$ Bohm values,
consistent with prior work on Tycho's SNR, whereas magnetic damping permits
magnetic fields of $\abt 10$--$300 \muG$ and comparatively smaller diffusion
coefficients (typically $\abt 1$--$10$).
Corresponding thin rim radio rims require magnetic damping, however.  We
jointly model radio and X-ray profiles and estimate magnetic damping length of
order $1$--$5$\% of remnant radius, with magnetic field strengths $\abt
50$--$400 \muG$ assuming Bohm diffusion.  Diffusion coefficients, magnetic
field strengths, and magnetic damping lengthscales are somewhat degenerate in
setting observed rim widths and drop-offs.
Although the energy dependence of synchrotron rims cannot discriminate magnetic
field structure, joint radio and X-ray modeling favors magnetic damping in
Tycho's SNR.
\end{abstract}

@@

@@

@@

@@

\begin{figure}
    \centering
    \iftoggle{manuscript}{
        \includegraphics[width=0.2\textwidth]{figures/snr.pdf}
    }{
        \plotone{figures/snr.pdf}
    }
    \caption{RGB image of Tycho with region selections overlaid.  Image bands
    are 0.7--1 keV (red), 1--2 keV (green) and 2--7 keV (blue).  Bold region
    labels (1, 16) indicate region selections shown in
    Figures~\ref{fig:spec},~\ref{fig:profiles}.  Filament 1: Regions 1--3,
    filament 2: regions 4--10, filament 3: regions 11-13, filament 4:
    regions 14--17, filament 5, regions 18--20.
    \label{fig:snr}}
\end{figure}
% NOTE keep region # bolding updated to match displayed filaments

@@

% NOTE keep blacklisted/excluded region count updated!
From the fitted profiles we extracted a full width at half maximum (FWHM) for
each region and each energy band after subtracting a constant background term
$\min(C_u, C_d)$.  We could not resolve a FWHM in 8 of 20 regions at 0.7--1 keV
(Table~\ref{tab:fwhms}); in these regions, either the downstream FWHM bound
would extend outside the fit domain or we could not find an acceptable fit to
equation~\eqref{eq:prof}.  We were able to resolve FWHMs for all regions at
higher energy bands (1--7 keV).

@@

% How we ran model fits (itemize knobs, explain energy band mapping, errors,
% fitting procedure
We fit model FWHM predictions given by Equation~ \eqref{eq:model} to our
measured rim widths as a function of energy by varying several physical
parameters: magnetic field strength $B_0$, normalized diffusion coefficient
$\eta_2$, diffusion-energy scaling exponent $\mu$, and minimum field strength
$\Bmin$ and lengthscale $a_b$ for a damped magnetic field scenario.  We
mapped each width measurement to the lower energy limit of its energy band;
e.g., $0.7$--$1 \unit{keV}$ is assigned to $0.7 \unit{keV}$ and fitted to model
profile widths at $0.7 \unit{keV}$.  Width errors in our least squares fits
average the positive and negative errors on each FWHM measurement.  For an
input set of model parameters, we numerically computed intensity profiles and
hence model FWHMs as detailed in Section~\ref{sec:transport}, and used a
Levenberg-Marquardt fitting routine to identify best fit model parameters.
To assist the nonlinear fitting, we tabulated model FWHM values on a large grid
of model parameters (primarily $\eta_2$ and $B_0$) and used best-fit grid as
initial guesses for fitting.
% TODO this may be obsoleted if we recompute stuff...  I only computed errors
% on the loss-limited model, and those fits are now out of date too...
%Errors on best fit parameters were computed by varying each fit parameter and
%obtaining a new best fit model, with one less degree of freedom, to find the
%parameter limit such that $\Delta \chi^2 = 1$ for a roughly 1-$\sigma$ error.

@@

% ----------------------------------------
% Constraining rims via radio measurements
% ----------------------------------------
\subsection{Radio rims require magnetic damping}

% Introduction
Thin radio rims spatially coincident with X-ray synchrotron rims may help
constrain magnetic field damping.  Radio emission in Tycho arises from the same
population of shock-accelerated electrons generating nonthermal X-ray rims.
But, $\abt$GeV electrons have cooling times of order $10^5$--$10^7 \unit{yr}$
in $10$--$100 \muG$ magnetic fields; synchrotron emission in the remnant
interior may reflect the spatial structure of long-lived electrons interacting
with a turbulent field rather than the advection of recently shock-accelerated
electrons.
Despite the extended population of radio synchrotron electrons, radio rims and
decreases in emission intensity immediately behind the shock may be explained
by magnetic damping.  If remnant-wide diffuse emission near the forward shock
increases monotonically towards the center of the remnant, only magnetic field
damping can cause emission to decrease.  A loss-limited field predicts
monotonically increasing emission downstream of the forward shock in our
steady-state transport model.
% TODO Redundant

% Procedure
We extract radio profiles from a $1.375 \unit{GHz}$ image of Tycho taken
with the VLA in A configuration in March 1994 (PI: D. Moffett); see
\citet{reynoso1997} for a detailed presentation.
\note[Aaron]{Was data from all configurations merged?  Done by \citet{reynoso1997}.}
The half-power beam width of $\abt 1.5\arcsec$ just resolves thin radio rims
and structure near the forward shock; the image is sampled at $0.5\arcsec$.
%We shift radio profiles forward following X-ray proper motion measurements by
%\citet{katsuda2010-tycho} over a 7 year baseline; the average shift is
%$\abt4.5\arcsec$.
Figure~\ref{fig:radio-snr} shows the extraction regions overlaying the radio
image and the previous X-ray profile regions of Figure~\ref{fig:snr}.

@@

% Procedure: model computation
To constrain magnetic field structure, we compare measured profiles to modeled
profiles from the transport model of equation~\eqref{eq:model} for varying
$B_0$ and $a_b$.  The parameters $B_{\mt{min}} = 5 \muG$, $\eta_2 = 1$, and
$\mu = 1$ are held fixed.  Diffusion, in particular, is negligible for modeled
radio emission as particle energies are 3 orders of magnitude lower than in
X-ray.  Neglecting diffusion also circumvents the unphysical assumption that
$D(x) B^2(x)$ is constant, which was invoked to obtain Green's function
solutions to equation~\eqref{eq:model}.

% Procedure: chi-by-eye "fitting"
We align model profiles to measurements by eye, varying relative amplitudes and
translations in radio and X-ray independently to best match the measured
profiles.  We manually vary $B_0$ and $a_b$ and attempt to reproduce both the
radio and X-ray rims.  Although ``fitting'' by eye cannot strongly constrain
model parameters, we can compute values of $B_0$ and $a_b$ consistent with the
observed profiles and qualitatively constrain magnetic damping throughout the
remnant.  Results from a more involved nonlinear fit may not be more reliable
as we cannot constrain spatially heterogeneous radio emission within
the remnant.  Moreover, our transport model neglects self-similar downstream
evolution of shocked plasma (decaying velocity, density, and magnetic field)
and is unreliable far downstream of the shock.

% Procedure: compare to previous work
The procedure we adopt for radio and X-ray modeling contrasts strongly with the
X-ray FWHM-width fitting, which neglected profile shape in favor of more robust
FWHM measurements.  Here, manually fitting profiles instead of FWHMs allows us
to consider radio and X-ray filaments that do not have well-defined FWHMs.
Radio rims consistently do not fall below 50\% of the peak emission.  We are
also able to use profiles from regions not previously considered due to the
lack of an X-ray FWHM, especially in softer ($0.7$--$4$) X-rays.

% Results: morphology, individual regions, main figure
We identify three classes of radio profiles: thin rims with downstream troughs,
plateaus, and continuous rises.  Regions B, C, D (southern limb) show plateaus
in radio emission.  Regions J, L, M (around NW) show continuous rises in
emission.  All other regions have a radio rim within $15\arcsec$ of the forward
shock, where the forward shock in radio is assumed at zero intensity.
Figure~\ref{fig:radio-prfs} shows extracted radio and nonthermal X-ray
($4$--$7\unit{keV}$) profiles for three well-fit regions with our best manually
selected model profiles, illustrating each of the three radio profile types
observed.

\begin{figure}
    \centering
    % Slightly larger figures than given by \plotone
    \includegraphics[width=0.46\textwidth]{figures/radio-fits-B.pdf} \\
    \includegraphics[width=0.46\textwidth]{figures/radio-fits-K.pdf} \\
    \includegraphics[width=0.46\textwidth]{figures/radio-fits-M.pdf}
    \caption{Measured radio and X-ray profiles plotted with model profiles for
    varying $a_b$ and $B_0$ in each region, showing typical parameters (and
    ranges) required to reproduce radio and X-ray rims simultaneously in our
    model.  Black solid curves in all regions plot our manually chosen best
    model profiles.  Profiles are chosen to show varying radio rim morphology,
    including plateaus (B), thin rims with troughs (K), and continuous rises
    (M); these profiles show some of the best agreement of our selected
    regions, but cf. Figure~\ref{fig:radio-prfs-meh}.  Profile radial
    coordinates are shifted arbitrarily to aid visual comparison (following
    proper motions of \citet{katsuda2010-tycho} where possible) but may not be
    physically meaningful.  Negative radio intensity is associated with
    deconvolution of raw VLA visibilities.
    \label{fig:radio-prfs}}
\end{figure}

% Results: linchpin for damping model here
A loss-limited rim model (constant magnetic field $B_0$) cannot produce thin
radio rims.  Our model requires damping length $a_b \lesssim 0.1$ to produce a
plateau or thin rim in radio emission.  For regions with thin radio rims, the
best manually selected profiles have $B_0$ between $50$--$400 \muG$, neglecting
only Region N which could not be modeled simultaneously in both X-ray and radio
(Figure~\ref{fig:radio-prfs-meh}).  The damping length $a_b$ ranges between
$0.01$--$0.03$, or $2$--$7\arcsec$.  The radio plateaus in regions B, C, D are
compatible with damping lengths between $0.01$--$0.05$.  Continuous rises in
radio emission are best modeled with $a_b \gtrsim 0.1$ and $B_0 \abt 200$--$300
\muG$.  Although damping lengths $a_b \gtrsim 0.1$ may not be physically
meaningful, such large values of $a_b$ yield practically constant magnetic
field behind the shock regardless.

% TODO what happens if \Bmin = 2 \muG?!

% Results: downstream emission should bound damping for an idealized,
% spherically symmetric remnant
The slope and depth of the radio emission decrease behind a thin rim also
gives a soft bound on the minimum magnetic field and maximum allowable damping
length, if other sources of radio emission increase monotonically downstream of
the shock and thus do not give rise to radio rims.  The maximum plausible $a_b$
is $\abt 0.01$--$0.05$ (1--5\% of shock radius, or $2$--$12\arcsec$); the
minimum magnetic field is $\abt 20 \muG$ assuming $\Bmin = 5 \muG$, at least
consistent with the expectation for a strong adiabatic shock.

\begin{figure}
    \centering
    \includegraphics[width=0.47\textwidth]{figures/radio-fits-I.pdf} \\
    \includegraphics[width=0.47\textwidth]{figures/radio-fits-N.pdf}
    \caption{Measured profiles that are less well-described by our model
    profiles, compared to Figure~\ref{fig:radio-prfs}.  Region I shows
    irregularly shaped radio rim.  Region N is a superposition of two filaments
    that cannot be simultaneously well-modeled in both X-ray and radio,
    requiring unrealistic magnetic fields or atypically small damping length to
    reproduce the emission plateau behind the radio thin rim.
    \label{fig:radio-prfs-meh}}
\end{figure}

% Discussion: confounding effects (and figure)
Tycho's shock structure is more complex than assumed by our transport model.
Moreover, emission in the remnant interior clearly shows spatial structure
(Figure~\ref{fig:radio-snr}).  Figure \ref{fig:radio-prfs-meh} shows two
regions that were poorly described by our model.  A majority of our regions
have irregular rims; in at least 2--3 regions, this may be attributed to
projection of multiple distinct filaments.  Others (e.g., Region K) show rims
with slopes that cannot be matched by our models, whether too steep or
shallow.  Shape mismatch may be attributed in part to point-spread mismatch,
diffusion (e.g., $\eta_2 \neq 1$), shock precursors, or other effects.

Nevertheless, our conclusion that thin radio rims require magnetic damping
should be robust and independent of model assumptions.
\citet{cassam-chenai2007}, for example, observed the same dichotomy in radio
emission for constant and damped magnetic fields in modeled profiles of Tycho's
shock from a self-similar hydrodynamic model with diffusive shock acceleration.
Our model captures the essential physics for a very young remnant such as
Tycho, for which the forward shock should be adiabatic.

% TODO We have NOT considered the relative intensities of X-ray / radio rims!

@@

The exponential variation in $D(x)$ (equation~\eqref{eq:ddamp}) may not be
physically reasonable; as we have noted above, the assumption $D(x)
\propto 1 / B^2(x)$ gives rise to sharp gradients in diffusion coefficient and
even inverts the effect of $\eta_2$ on our model profiles (where larger
$\eta_2$ can cause rim widths to narrow).  Nevertheless, the modeled behavior
is physically reasonable.  And, only X-ray profiles are impacted by the
assumption on $D(x)$ as radio profiles assume no diffusion.

@@

We measured the widths of several thin synchrotron filaments around Tycho's
supernova remnant and found moderate narrowing of rim widths throughout the
remnant, corroborating rim narrowing observed by \citet{ressler2014} in the
remnant of SN 1006.  We confirmed that selected filaments are dominated by
nonthermal emission and have clearly measurable full widths at half maximum in
4--5 energy bands.

A steady-state particle transport model with constant magnetic field gives
diffusion coefficients and magnetic field strengths broadly consistent with
prior estimates from rim widths \citep[e.g.,][]{parizot2006, rettig2012} and
radio and gamma ray measurements \citep{acciari2011, morlino2012}.  The same
model with a damped magnetic field is equally capable of describing our
measured data.  At weak energy dependence the two models are indistinguishable
and magnetic damping fits still favor moderately amplified magnetic fields.  At
moderate energy dependence ($\mE \sim -0.3$), the damping model favors weaker
magnetic fields, but modeled FWHMs may not be truly representative of thin rim
widths and profiles.

Thin radio synchrotron rims, however, can only be produced at the shock by
magnetic damping.  Assuming shocked electrons account for most radio emission
immediately downstream of Tycho's forward shock, we jointly model radio and
X-ray profiles to measured profiles and find that damping lengths of $1$--$5$\%
of the shock radius are required throughout most of the remnant; only a few
(3/16) selected regions are plausibly consistent with a constant advected
magnetic field.  Typical magnetic field strengths range between $50$--$400
\muG$.  Although we cannot bound damping lengths and fields from our
qualitative profile comparisons, our results are physically reasonable and are
likely good to order-of-magnitude.

%Additional proxies for diffusion and/or magnetic field are needed to better
%constrain magnetic damping in the shocks of young supernova remnants.
%
%As our data are not count limited, we suggest that additional proxies for
%diffusion and magnetic field are needed to establish or rule out the presence
%of damping at the shocks of young supernova remnants.  More sophisticated
%modeling of shock physics \citep[e.g.,][]{zirakashvili2014} and shock/filament
%structure \citep[cf.][]{caprioli2013} may be necessary to improve modeling
%results.

@@

A.T. thanks CRESST for sponsorship/support at GSFC (any relevant grants?)
We thank David Moffett for providing the VLA image used in this study.
The scientific results reported in this article are based on data obtained from
the \Chandra Data Archive.
This research made extensive use of NASA's Astrophysics Data System.
This research also made use of APLpy, an open-source plotting package for
Python hosted at \href{http://aplpy.github.com}{http://aplpy.github.com}.

@@

Here we give best loss-limited and damped fit results for averaged filament
widths in SN 1006, taken from \citet{ressler2014}.
